---
title: "Q1 function Prediction"
author: "Brett Kroncke"
date: "September 19, 2017"
output: 
  pdf_document: 
    highlight: pygments
    toc: true
    toc_depth: 4
---

# Introduction
This document is meant to assess the utility of structure-based features to predict functional perturbation of missense variants in kcnq1.

## Read in data

```{r setup, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# load all required libraries
library(sjstats)
library(caret)
library(plotrix)
library(glmnet)
library(meta)
library(reshape2)
library(psych)
require(Hmisc)
library(tableone)
library(ggplot2)
library("DBI")
library("RSQLite")
library(wCorr)
library(rms)
library(boot)
library(leaps)
library(car)
library(reticulate)
source('C:/Users/Brett/Dropbox/SCN5A/predict_function/func_dist.R')

# import the picked file with nested dictionaries of 
# distances between residue centriods.
p <- import("pickle")
py <- import_builtins()
distances <- p$load(py$open(
  'C:/Users/Brett/Dropbox/SCN5A/predict_function/KCNQ1/data/Q1_noCaM/Q1_save_noCaM.p', "rb"))

# figure path and data path
feat.path <- "C:/Users/Brett/Dropbox/SCN5A/predict_function/KCNQ1/data/" # also has the target file

# load data
targ <- "Q1_noCaM/Q1DatasetJan07_revised.csv"
f <- "pph2-short.csv"
fs <- "sift.csv"

fpph2 <- read.csv(paste(feat.path,f, sep=""), header = TRUE)
fsift <- read.csv(paste(feat.path,fs, sep=""), header = TRUE)
e <- read.csv(paste(feat.path,targ, sep=""), header = TRUE)

f <- merge(fpph2,e, all = T)
f <- f[!is.na(f$erate),]
f <- unique(f)
d <- merge(fsift,f, all = T)
d <- d[!is.na(d$erate),]
d <- unique(d)

#d$LOF <- NA
d$LOF[d$Ikspeak<0.50 | d$Vhalfact >= 20] <- 1
#d$LOF[d$Vhalfact >= 20] <- 1
d$LOF[d$Ikspeak>=0.50 & d$Vhalfact < 20 ] <- 0

functions <- c("Ikspeak", "Vhalfact", "tau_act", "tau_deact")
comps <- c("pamscore", "SIFT.Score", "erate", "blast", "provean_score", "pph2_prob", "NeighborVector", "NeighborCount", "aaneigh", "aaneighvector")

clinvar.path <- "C:/Users/Brett/Dropbox/SCN5A/predict_function/paper/"
clinvar <- read.csv(paste(clinvar.path,"kcnq1_clinvar.csv", sep=""), header = TRUE)
g <- merge(clinvar,d, all = T)
g <- g[!is.na(g$erate),]
g <- unique(g)
write.csv(g,"C:/Users/Brett/Dropbox/SCN5A/predict_function/paper/TableQ1.csv")

```

## Plot LOESS and Dots Function

```{r functions, echo=TRUE}

plt.loess <- function(fit, xlabel="X", ylabel="Y", xlims=NA, ylims=NA){
  if(sum(is.na(xlims) & is.na(ylims))>0){
    lines(min(fit$x)-1000, 0, xlim=c(min(fit$x), max(fit$x)), ylim=c(min(fit$y), max(fit$y)), ylab=ylabel, xlab=xlabel)
  } else{ if(is.na(xlims)){
    lines(min(fit$x)-1000, 0, xlim=c(min(fit$x), max(fit$x)), ylim=ylims, ylab=ylabel, xlab=xlabel)
  } else{
    lines(min(fit$x)-1000, 0, xlim=xlims, ylim=ylims, ylab=ylabel, xlab=xlabel)
  }
  }
  xrange <- seq(min(fit$x), max(fit$x), length.out = 100)
  ps <- predict(fit, xrange, se=T)
  lines(xrange, ps$fit*1, lwd=5)
  lines(xrange, (ps$fit+1.96*ps$se.fit)*1, lty=2, lwd=4)
  lines(xrange, (ps$fit-1.96*ps$se.fit)*1, lty=2, lwd=4)
}

```

# Summary Statistics

```{r table1}
vari <- c("Ikspeak","Vhalfact", "tau_act", "tau_deact")
t1 <- CreateTableOne(vars = vari, data=d)
print(t1, nonnormal=vari)
```

# Histograms of Functional Parameters

```{r histograms}
hist(d$Ikspeak, breaks = 20)
hist(d$Vhalfact, breaks = 20)
hist(log10(d$tau_act), breaks = 20)
hist(log10(d$tau_deact), breaks = 20)
```

# Histogram of Distance Distributions

```{r dist_hist}
tmp <- unlist(distances)
tmpp <- hist(tmp[tmp<=20], probability = T, breaks = 100)
hist(tmp[tmp<=20], probability = T, breaks = 100)
axis(side=1, at=seq(0,20,1))
plot(tmpp$breaks[-c(1,2)],tmpp$density[-1]/(tmpp$breaks[-c(1,2)]^2), type="o", ylab = "Density", xlab = "Distance")
# looks like maxima at 6.5, 11, and 15
```

# Calculate functional densities

```{r calc_func_dists}

for (EP_function in functions){
  feat_dist <- paste(EP_function, "_dist", sep = "")
  feat_dist_weight <- paste(EP_function,"_dist_weight", sep = "")
  d[, feat_dist]<-NA
  d[, feat_dist_weight]<-NA
  for(rec in 1:nrow(d)){
    d[rec, c(feat_dist, feat_dist_weight)] <- funcdist(d[rec, "resnum"], d[rec, "mutAA"], d, distances, EP_function, "sigmoid", 7)
  }
}
```

# Heatmap of Pearson R values (absolute values)

```{r heatmap, echo=TRUE}
# select all covariates and responses I want to analyze 
dists <- d[!is.na(d$Ikspeak_dist), c(functions, paste(functions,"_dist",sep = ""),
                                     comps,
                                   paste(functions,"_dist_weight",sep = ""))]

# Make pearson correlation matrix of calculated vs. experimental functional 
# parameters and some in silico predicive models. Plot heatmap of R values
mat = data.matrix(dists) # corr.test needs a matrix

rcor<-corr.test(mat,use='pairwise.complete.obs', method = 'pearson')
rcor$r<-(rcor$r)^2

# make ggplot object
p<-ggplot(melt(rcor$r), aes(Var1,ordered(Var2, levels = rev(sort(unique(Var2))))))+ geom_tile(aes(fill = value), color = "white") + scale_fill_gradient(low = "white", high = "steelblue") 

#ordered(Var2, levels = rev(sort(unique(Var2))))
base_size<-9
p+ theme_grey(base_size = base_size) + labs(x = "", y = "") + 
  scale_x_discrete(expand = c(0, 0)) + 
  scale_y_discrete(expand = c(0, 0)) + theme(legend.position = "none", axis.text.x.top = element_text(angle = 90, vjust=0.5, hjust=0)) + scale_x_discrete(position = "top")

```

# Linear Models Predicting Functional Features
Test several different models, including a few feature sets. Include 95% CI intervals on Pearson R^2.

## Iks Peak Current

### Predict Iks Current Using Exhaustive Model Selection

```{r LASSO_ikspeak}

d2 <- d[, which(names(d) %in% c("Ikspeak", "Ikspeak_dist", "Ikspeak_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="Ikspeak")]), d2$Ikspeak, type.measure = "deviance") 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="Ikspeak")]), d2$Ikspeak, lambda = cv.lass$lambda.min)  
fin.lass$beta


```


```{r LASSO_peak_CV_modelling}

LASSO_CV(d,10,comps,"Ikspeak")
#June 12, 2018: mean  0.208901679465561  95% CI:  0.0679620959545628 ,  0.426957509126576

```

### Predicting Iks using Best Predictors found in Previous Step and bootstrap 95% CIs

```{r iks_lm, echo=TRUE}
# all predictors
ln_peak <- lm(Ikspeak~., data = d2[, c("Ikspeak", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_peak)
foo <- boot(d, function(data,indices)
  summary(lm(Ikspeak~., data = d2[indices, c("Ikspeak", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

eta_sq(anova(ln_peak))

```

### Plot Data of Iks and Features from the Above Model Selection

```{r Iks_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(d2$blast, d2$Ikspeak*100, cex=2, lwd=2, xlim = c(0,15), ylim = c(0,325))
plt.loess(loess(d2$Ikspeak*100~as.numeric(d2$blast), span=0.7),ylabel= "Peak Current")

plot(d2$Ikspeak_dist*100, d2$Ikspeak*100, cex=2, lwd=2, xlim = c(0,150), ylim = c(0,325))
plt.loess(loess(d2$Ikspeak*100~as.numeric(d2$Ikspeak_dist*100), span=0.7),ylabel= "Peak Current")

#plot(d$blast, d$Ikspeak*100, cex=2, lwd=1, xlim = c(-5,20))
#plt.loess(loess(d$Ikspeak*100~as.numeric(d$blast), span=0.7),ylabel= "Peak Current")

```

### Plot Predicted and Experimetal Iks Peak Current

```{r iks_exp_pred}
plot(ln_peak$fitted.values*100,ln_peak$model$Ikspeak*100, ylim = c(0,max(ln_peak$model$Ikspeak*100)), xlim = c(0, max(ln_peak$model$Ikspeak*100)),cex=2, lwd=1)
abline(a=0,b=1)

#plot(d$bcl_ikspeak*100,d$Ikspeak*100, ylim = c(0,max(d$Ikspeak*100, na.rm = T)), xlim = c(0, max(d$Ikspeak*100, na.rm = T)),cex=2, lwd=1)
#abline(a=0,b=1)

```

## Iks Vhalf Activation

### Predict Vhalf Activation Using Exhaustive Model Selection

```{r LASSO_vhalfact}

d2 <- d[, which(names(d) %in% c("Ikspeak", "Vhalfact", "Vhalfact_dist", "Vhalfact_dist_weight", comps))]
#d2 <- d2[d2$Ikspeak>0.15,]
d3 <- d2[, which(names(d2) %in% c("Vhalfact", "Vhalfact_dist", "Vhalfact_dist_weight", comps))]
d2 <- d3[complete.cases(d3),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="Vhalfact")]), d2$Vhalfact) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="Vhalfact")]), d2$Vhalfact, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

```{r LASSO_Vhalfact_CV_modelling}

LASSO_CV(d,10,comps,"Vhalfact")
#June 13, 2018: mean  0.224923083006987  95% CI:  0.0951057405108745 ,  0.409765063318065

```

### Predicting Vhalf Activation using Best Predictors found in Previous Step and bootstrap 95% CIs

```{r vhalfact_lm, echo=TRUE}
# all predictors
ln_vact <- lm(Vhalfact~., data = d2[, c("Vhalfact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_vact)
foo <- boot(d, function(data,indices)
  summary(lm(Vhalfact~., data = d2[indices, c("Vhalfact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

eta_sq(ln_vact)
# Below estimates partial variance explained but is sensitive to order (so I'm not using it, but it's still interesting).
#af <- anova(ln_vact)
#afss <- af$`Sum Sq`
#cbind(af,PctExp=afss/sum(afss)*100)
```

### Plot Data of Vhalf Activation and Features from the Above Model Selection

```{r vhalf_act_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
# vhalfact_dist+blast+aa_pair_interaction1+aaneighvector+pamscore+mtr

plot(d$pph2_prob, d$Vhalfact, cex=2, lwd=2)
plt.loess(loess(d$Vhalfact~as.numeric(d$pph2_prob), span=0.7),ylabel= "Peak Current")

plot(d$Vhalfact_dist, d$Vhalfact, cex=2, lwd=2)
plt.loess(loess(d$Vhalfact~as.numeric(d$Vhalfact_dist), span=0.7),ylabel= "Peak Current")

```

### Plot Predicted and Experimetal Iks V half Activation

```{r Vhalfact_exp_pred}
plot(ln_vact$fitted.values,ln_vact$model$Vhalfact, ylim = c(min(ln_vact$model$Vhalfact), max(ln_vact$model$Vhalfact)), xlim = c(min(ln_vact$model$Vhalfact), max(ln_vact$model$Vhalfact)),cex=2, lwd=1)
abline(a=0,b=1)

#plot(d$bcl_vhalfact,d$Vhalfact, ylim = c(min(d$Vhalfact,na.rm = T),max(d$Vhalfact,na.rm = T)), xlim = c(min(d$Vhalfact,na.rm = T), max(d$Vhalfact,na.rm = T)),cex=2, lwd=1)
#abline(a=0,b=1)
```

## Iks Characteristic Activation Time (tau_act)
Not high enough adjusted R^2 to bother persuing.  

### Predict Characteristic Activation Time (tau_act) Using Exhaustive Model Selection

```{r LASSO_tau_act}

d2 <- d[, which(names(d) %in% c("tau_act", "tau_act_dist", "tau_act_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="tau_act")]), d2$tau_act) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="tau_act")]), d2$tau_act, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

```{r LASSO_tau_act_CV_modelling}

LASSO_CV(d,10,comps,"tau_act")
#June 13, 2018: 

```

### Predicting Iks Characteristic Activation Time (tau_act) using Best Predictors found in Previous Step and bootstrap 95% CIs

```{r tau_act_lm, echo=TRUE}
# all predictors
ln_tau_act <- lm(tau_act~., data = d2[, c("tau_act", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_tau_act)
foo <- boot(d, function(data,indices)
  summary(lm(tau_act~., data = d2[indices, c("tau_act", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))
```

## Iks Characteristic Deactivation Time (tau_deact)

### Predict Characteristic Deactivation Time (tau_deact) Using Exhaustive Model Selection

No predictors were kept. 

```{r LASSO_tau_deact}

d2 <- d[, which(names(d) %in% c("tau_deact", "tau_deact_dist", "tau_deact_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="tau_deact")]), d2$tau_deact) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="tau_deact")]), d2$tau_deact, lambda = cv.lass$lambda.min)  
fin.lass$beta


```

```{r LASSO_tau_deact_CV_modelling}

LASSO_CV(d,10,comps,"tau_deact")
#June 13, 2018: 

```

### Predicting tau_deact using Best Predictors found in Previous Step and bootstrap 95% CIs

```{r tau_deact_lm, echo=TRUE}
# all predictors
ln_tau_act <- lm(tau_deact~., data = d2[, c("tau_deact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_tau_act)
foo <- boot(d, function(data,indices)
  summary(lm(tau_deact~., data = d2[indices, c("tau_deact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

```

### Plot Data of tau_deact and Features from the Above Model Selection

```{r tau_deact_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
# erate+aa_pair_interaction1+aaneigh_rank_sses+aaneigh
plot(d$aa_pair_interaction1, log10(d$tau_deact), cex=2, lwd=2)
plt.loess(loess(log10(d$tau_deact)~as.numeric(d$aa_pair_interaction1), span=0.7),ylabel= "Peak Current")

plot(d$erate, log10(d$tau_deact), cex=2, lwd=1)
plt.loess(loess(log10(d$tau_deact)~as.numeric(d$erate), span=0.7),ylabel= "Peak Current")

plot(d$aaneigh_rank_sses, log10(d$tau_deact), cex=2, lwd=1)
plt.loess(loess(log10(d$tau_deact)~as.numeric(d$aaneigh_rank_sses), span=0.9),ylabel= "Peak Current")

plot(d$aaneigh, log10(d$tau_deact), cex=2, lwd=1)
plt.loess(loess(log10(d$tau_deact)~as.numeric(d$aaneigh), span=0.7),ylabel= "Peak Current")
```

### Plot Predicted and Experimetal Iks Deactivation time

```{r tau_deact_exp_pred}
plot(ln_tau_deact$fitted.values,ln_tau_deact$model$tau_deact)
abline(a=0,b=1)
```

# ROCs for predicting LOF based on ipeak current < 50%

```{r ROCs}
fglm<-d[!is.na(d$Ikspeak_dist), ]
modfunc <- glm(LOF~aaneigh+blast+erate+pph2_prob, data = fglm, family = 'binomial')

source("/Users/Brett/Dropbox/SCN5A/jeff roc fnc.r")
mod <- glm(LOF~blast+erate+pph2_prob, data=fglm, family='binomial')
summary(mod)


roc.ci(d$LOF[row.names(d) %in% as.numeric(names(predict(modfunc)))], predict(modfunc))

roc.ci(d$LOF[row.names(d) %in% as.numeric(names(predict(mod)))], predict(mod), add = T)

#bootstrap 95% CIs

library(pROC)
modfunc1 <- glm(LOF~pph2_prob, data = fglm, family = 'binomial')
modfunc2 <- glm(LOF~erate, data = fglm, family = 'binomial')
modfunc3 <- glm(LOF~blast, data = fglm, family = 'binomial')
modfunc4 <- glm(LOF~provean_score, data = fglm, family = 'binomial')
modfunc5 <- glm(LOF~blast+erate+pph2_prob+provean_score, data = fglm, family = 'binomial')
modfunc6 <- glm(LOF~Ikspeak_dist+Vhalfact_dist+blast+erate+pph2_prob+provean_score, data = fglm, family = 'binomial')

funs <- list(modfunc2, modfunc3, modfunc4, modfunc5, modfunc6)
colrs <- c("red", "green", "orange", "blue", "black")
i=0
par(pty="s")
tmp<-roc(d$LOF[row.names(d) %in% as.numeric(names(predict(modfunc1)))], predict(modfunc1), ci = T)
print(tmp$auc)
print(tmp$ci)
plot.roc(tmp, col = "magenta")
for(li in funs){
  i=i+1
  tmp<-roc(d$LOF[row.names(d) %in% as.numeric(names(predict(li)))], predict(li), ci=T)
  print(tmp$auc)
  print(tmp$ci)
  plot.roc(tmp,add = T, col = colrs[i])
}
```