---
title: "Predict SCN5A Variant Function Using Structure and *In Silico* Features"
author: "B"
date: "January 23, 2018"
output: 
  pdf_document: 
    highlight: pygments
    toc: true
    toc_depth: 4
---

# Introduction
This document is meant to assess how well we can predict functional perturbation from SCN5A missense variants. We're especially interested in the contribution of structure-based features. 

## Notes:

Should I report non-transformed ilate and recovfrominact as well as log transformed? Why not? These were tried and did not contribute to any difference.

## Read Data
```{r load, echo = TRUE}
# load all required libraries
library(caret)
library(plotrix)
library(glmnet)
library(meta)
library(reshape2)
library(psych)
require(Hmisc)
library(tableone)
library(ggplot2)
library("DBI")
library("RSQLite")
library(wCorr)
library(rms)
library(boot)
library(leaps)
library(car)
library(reticulate)
source('C:/Users/Brett/Dropbox/SCN5A/predict_function/func_dist.R')

# import the picked file with nested dictionaries of 
# distances between residue centriods.
p <- import("pickle")
py <- import_builtins()
distances <- p$load(py$open(
  'C:/Users/Brett/Dropbox/SCN5A/predict_function/data/5A_5x0m/5A_save_5x0m.p', "rb"))

# figure path and data path
feat.path <- "C:/Users/Brett/Dropbox/SCN5A/predict_function/data/" # also has the target file

# load data
targ <- "C:/Users/Brett/Dropbox/SCN5A/BrettsSandbox/paper/resubmit/TableS2.csv"
new <- "5A_5x0m/sin_pam_energy_funcdist.csv"
bcl  <- read.csv("/Users/Brett/Dropbox/SCN5A/predict_function/data/5A_5x0m/scn5a_bcl_features_5x0m.txt", header = TRUE, sep = "\t")
sasa <- read.csv("/Users/Brett/Dropbox/SCN5A/predict_function/data/5A_5x0m/5a_5x0m_sasa.csv", header = TRUE)
d <- read.csv(targ, header = TRUE)
colnames(d)[1] <- "var"
e <- read.csv(paste(feat.path,new, sep=""), header = TRUE)
d <- merge(d,e, all = TRUE)
d <- d[d$mut_type == "missense" | d$mut_type == "aadel" | d$mut_type == "aains",]
d <- unique(d)
d <- merge(d,bcl, all = TRUE)
d <- merge(d,sasa, all = TRUE)
d <- d[!is.na(d$var),]
d <- unique(d)
#d <- d[!is.na(d$aaneigh),]
d$recovfrominact<-10^(d$recovfrominact)
d$ilate<-10^(d$ilate)
#d$ilate_norm<-10^(d$ilate_norm)


d$LOF <- NA
d$LOF[d$ipeak>=50] <- 0
d$LOF[d$ipeak<50 | d$vhalfact > 10] <- 1

#d <- d[,c(1:21,24:58,22:23)]
#d <- d[,c(1:4,6:58,5)]
#d <- d[d$total_carriers>3,]

functions <- c("ipeak", "ilate", "vhalfact", "vhalfinact", "recovfrominact")
comps <- c("NeighborVector", "NeighborCount", "aaneigh", "aaneighvector", "pamscore", "SIFT", "eaRate", "blastpssm",  "provean_score", "polyphen2")

clinvar.path <- "C:/Users/Brett/Dropbox/SCN5A/predict_function/paper/"
clinvar <- read.csv(paste(clinvar.path,"scn5a_clinvar.csv", sep=""), header = TRUE)
g <- merge(clinvar,d, all = T)
g <- g[!is.na(g$var),]
g <- unique(g)
write.csv(g,"C:/Users/Brett/Dropbox/SCN5A/predict_function/paper/Table5A_clinvar.csv")

```

## Summary Statistics

```{r table1}
vari <- c(functions,"ilate_norm")
t1 <- CreateTableOne(vars = vari, data=d)
print(t1, nonnormal=vari)
```

## Functions: Plot LOESS with Points

```{r functions, echo=TRUE}

plt.loess <- function(fit, xlabel="X", ylabel="Y", xlims=NA, ylims=NA){
  if(sum(is.na(xlims) & is.na(ylims))>0){
    lines(min(fit$x)-1000, 0, xlim=c(min(fit$x), max(fit$x)), ylim=c(min(fit$y), max(fit$y)), ylab=ylabel, xlab=xlabel)
  } else{ if(is.na(xlims)){
    lines(min(fit$x)-1000, 0, xlim=c(min(fit$x), max(fit$x)), ylim=ylims, ylab=ylabel, xlab=xlabel)
  } else{
    lines(min(fit$x)-1000, 0, xlim=xlims, ylim=ylims, ylab=ylabel, xlab=xlabel)
  }
  }
  xrange <- seq(min(fit$x), max(fit$x), length.out = 100)
  ps <- predict(fit, xrange, se=T)
  lines(xrange, ps$fit*1, lwd=5)
  lines(xrange, (ps$fit+1.96*ps$se.fit)*1, lty=2, lwd=4)
  lines(xrange, (ps$fit-1.96*ps$se.fit)*1, lty=2, lwd=4)
}

```

## Histograms of functional parameters

```{r histograms}
hist(d$ipeak, breaks = 20)
hist(d$vhalfact, breaks = 20)
hist(d$vhalfinact, breaks = 20)
hist(log10(d$recovfrominact), breaks = 20)
hist(log10(d$ilate), breaks = 20)

```

# Histogram of Distance Distributions

```{r dist_hist}
tmp <- unlist(distances)
tmpp <- hist(tmp[tmp<=20], probability = T, breaks = 100)
hist(tmp[tmp<=20], probability = T, breaks = 100)
axis(side=1, at=seq(0,20,1))
plot(tmpp$breaks[-c(1,2)],tmpp$density[-1]/(tmpp$breaks[-c(1,2)]^2), type="o", ylab = "Density", xlab = "Distance")
# looks like maxima at 6.5, 11, and 15
```

# Calculate functional densities

```{r calc_func_dists}

for (EP_function in functions){
  feat_dist <- paste(EP_function, "_dist", sep = "")
  feat_dist_weight <- paste(EP_function,"_dist_weight", sep = "")
  d[, feat_dist]<-NA
  d[, feat_dist_weight]<-NA
  for(rec in 1:nrow(d)){
    d[rec, c(feat_dist, feat_dist_weight)] <- funcdist(d[rec, "resnum"], d[rec, "mutAA"], d, distances, EP_function, "sigmoid", 7)
  }
}
```

# Heatmap of Pearson R values (absolute values)

```{r heatmap, echo=TRUE}
# select all covariates and responses I want to analyze 
dists <- d[!is.na(d$ipeak_dist), c(functions, paste(functions,"_dist",sep = ""),comps,
                                   paste(functions,"_dist_weight",sep = ""))]

# Make pearson correlation matrix of calculated vs. experimental functional 
# parameters and some in silico predicive models. Plot heatmap of R values
mat = data.matrix(dists) # corr.test needs a matrix

rcor<-corr.test(mat,use='pairwise.complete.obs', method = 'pearson')
rcor$r<-(rcor$r)^2

# make ggplot object
p<-ggplot(melt(rcor$r), aes(Var1,ordered(Var2, levels = rev(sort(unique(Var2))))))+ geom_tile(aes(fill = value), color = "white") + scale_fill_gradient(low = "white", high = "steelblue") 

#ordered(Var2, levels = rev(sort(unique(Var2))))
base_size<-9
p+ theme_grey(base_size = base_size) + labs(x = "", y = "") + 
  scale_x_discrete(expand = c(0, 0)) + 
  scale_y_discrete(expand = c(0, 0)) + theme(legend.position = "none", axis.text.x.top = element_text(angle = 90, vjust=0.5, hjust=0)) + scale_x_discrete(position = "top")

```

# Linear Models Predicting Functional Features
Test several different models, including a few feature sets. Include 95% CI intervals on Pearson R^2.

## Peak Current

### Parameter Selection for Peak Current Model

```{r LASSO_peak}

d2 <- d[, which(names(d) %in% c("ipeak", "ipeak_dist", "ipeak_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="ipeak")]), d2$ipeak) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="ipeak")]), d2$ipeak, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

```{r LASSO_peak_CV_modelling}

LASSO_CV(d,10,comps,"ipeak")
#June 11, 2018: mean  0.229844408389791  95% CI:  0.0950763623663287 ,  0.423146694973547

```

### Predicting ipeak with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r ipeak_lm}
# all predictors
ln_peak <- lm(ipeak~., data = d2[, c("ipeak", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_peak)
foo <- boot(d, function(data,indices)
  summary(lm(ipeak~., data = d2[indices, c("ipeak", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

```

### Plot Experimental Functional Parameters Against Predictive Features

```{r ipeak_raw_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(d$ipeak_dist, d$ipeak, cex=2, lwd=2, xlim = c(0,125), ylim = c(0,250))
plt.loess(loess(d$ipeak~as.numeric(d$ipeak_dist), span=0.7),ylabel= "Peak Current")

plot(d$pamscore, d$ipeak, cex=2, lwd=1, xlim = c(-11,3), ylim = c(0,250))
plt.loess(loess(d$ipeak~as.numeric(d$pamscore), span=0.7),ylabel= "Peak Current")

plot(d$polyphen2, d$ipeak, cex=2, lwd=1, ylim = c(0,250))
plt.loess(loess(d$ipeak~as.numeric(d$polyphen2), span=0.7),ylabel= "Peak Current")
```

### Plot Predicted and Experimental Peak Current

```{r ipeak_exp_pred, fig.height=8, fig.width=8}
plot(ln_peak$fitted.values,ln_peak$model$ipeak, ylim = c(0,max(ln_peak$model$ipeak)), xlim = c(0, max(ln_peak$model$ipeak)),cex=2, lwd=1)
abline(a=0,b=1)
```


## Late Current

Models are not good when ilate is linear, not transformed exponentially: LASSO doesn't want to keep any features, at least not consistantly. We have the same problem when ilate is log transformed.

### Parameter Selection for Late Current Model

```{r LASSO_ilate}

d2 <- d[, which(names(d) %in% c("ilate", "ilate_dist", "ilate_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="ilate")]), d2$ilate) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="ilate")]), d2$ilate, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

```{r LASSO_ilate_CV_modelling}
# Too volatile, selects 0 features at times. 
LASSO_CV(d,10,comps,"ilate")

```

### Predicting ilate with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r ilate_lm}
# all predictors
ln_late <- lm(ilate~., data = d2[, c("ilate", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_late)
foo <- boot(d, function(data,indices)
  summary(lm(ilate~., data = subset(d2[indices, c("ilate", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])))$adj.r.squared,R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

```

### Plot Predicted and Experimental Functional Parameters

```{r ilate_raw_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(d$blast, d$ilate, cex=2, lwd=2)
plt.loess(loess(d$ilate~as.numeric(d$blast), span=0.7),ylabel= "Peak Current")

plot(d$NeighborCount, d$ilate, cex=2, lwd=1)
plt.loess(loess(d$ilate~as.numeric(d$NeighborCount), span=0.7),ylabel= "Peak Current")

```

### Plot Predicted and Experimental Late Current

```{r ilate_exp_pred, fig.height=8, fig.width=8}
plot(log10(ln_late$fitted.values),log10(ln_late$model$ilate))
abline(a=0,b=1)
```


## Vhalf Activation
Result isn't stable through CV with LASSO.

### Parameter Selection for Vhalf Activation Model

```{r LASSO_vhalfact}

d2 <- d[, which(names(d) %in% c("vhalfact", "vhalfact_dist", "vhalfact_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="vhalfact")]), d2$vhalfact) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="vhalfact")]), d2$vhalfact, lambda = cv.lass$lambda.min)  
fin.lass$beta


```

```{r LASSO_vhalfact_CV_modelling}
# very volatile again.
LASSO_CV(d,10,comps,"vhalfact")

```

### Predicting Vhalf Activation with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r vact_lm}
# all predictors
ln_vact <- lm(vhalfact~., data = subset(d2, select = c(vhalfact, 1+fin.lass$beta@i)))
summary(ln_vact)
foo <- boot(d, function(data,indices)
  summary(lm(vhalfact~., data = subset(d2[indices,], select = c(vhalfact,1+fin.lass$beta@i))))$adj.r.squared,R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))


```


## Vhalf Inactivation

### Parameter Selection for Vhalf Inactivation Model

```{r LASSO_vhalfinact}

d2 <- d[, which(names(d) %in% c("vhalfinact", "vhalfinact_dist", "vhalfinact_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="vhalfinact")]), d2$vhalfinact) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="vhalfinact")]), d2$vhalfinact, lambda = cv.lass$lambda.min)  
fin.lass$beta


```

```{r LASSO_vhalfinact_CV_modelling}

LASSO_CV(d,10,comps,"vhalfinact")
#mean  0.117180420884853  95% CI:  0.0606976335554824 ,  0.192075000486572

```

### Predicting Vhalf Inactivation with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r vinact_lm}
# all predictors
ln_peak <- lm(vhalfinact~., data = d2[, c("vhalfinact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_peak)
foo <- boot(d, function(data,indices)
  summary(lm(vhalfinact~., data = d2[indices, c("vhalfinact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

#[1] 0.1681157
#      2.5%      97.5% 
#0.08298256 0.34876562 

```

### Plot Predicted and Experimental Functional Parameters

```{r vinact_raw_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(d$vhalfinact_dist, d$vhalfinact, cex=2, lwd=2)
plt.loess(loess(d$vhalfinact~as.numeric(d$vhalfinact_dist), span=0.7),ylabel= "Peak Current")

#plot(d$polyphen2, d$vhalfinact, cex=2, lwd=1, xlim = c(-5,10))
#plt.loess(loess(d$vhalfinact~as.numeric(d$polyphen2), span=0.7),ylabel= "Peak Current")


```

### Plot Predicted and Experimental Vinact

```{r vinact_exp_pred}
plot(ln_vinact$fitted.values,ln_vinact$model$vhalfinact)
abline(a=0,b=1)
```


## Recovery from Inactivation

LASSO doesn't keep covariates consistantly when recovfrominact is not transformed. Same problem when data are log10 transformed 

### Parameter Selection for Recovery from Inactivation Model

```{r LASSO_recov}

d2 <- d[, which(names(d) %in% c("recovfrominact", "recovfrominact_dist", "recovfrominact_dist_weight", comps))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="recovfrominact")]), d2$recovfrominact) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="recovfrominact")]), d2$recovfrominact, lambda = cv.lass$lambda.min)  
fin.lass$beta


```

```{r LASSO_recovfrominact_CV_modelling}

LASSO_CV(d,10,comps,"recovfrominact")

```

### Predicting Recovery from Inactivation with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r recov_lm}
# all predictors
ln_recov <- lm(recovfrominact~., data = d2[, c("recovfrominact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])])
summary(ln_recov)
foo <- boot(d, function(data,indices)
  summary(lm(recovfrominact~., data = d2[indices, c("recovfrominact", fin.lass$beta@Dimnames[[1]][1+fin.lass$beta@i])]))$adj.r.squared, R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))

```

### Plot Predicted and Experimental Functional Parameters

```{r recov_raw_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(log10(d$recovfrominact_dist+0.001), log10(d$recovfrominact), cex=2, lwd=2)
plt.loess(loess(log10(d$recovfrominact)~log10(as.numeric(d$recovfrominact_dist+0.001)), span=0.7),ylabel= "Peak Current")

```

### Plot Predicted and Experimental Recovery from Inactivation

```{r recovinact_exp_pred, fig.height=8, fig.width=8}
plot(ln_recov$fitted.values,ln_recov$model$recovfrominact)
abline(a=0,b=1)
```

# Predicting Penetrance

## BrS1

### Parameter Selection for BrS1 Model

```{r LASSO_BrS1}

d2 <- d[, which(names(d) %in% c( "brs1_penetrance_dist","brs1_penetrance_dist_weight", "pamscore", "SIFT.Score", "eaRate", "blastpssm", "NeighborVector", "NeighborCount",
        "provean_score", "polyphen2", "aaneigh", "aaneighvector","BrS_penetranceBayesian", "resnum"))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="BrS_penetranceBayesian")]), d2$BrS_penetranceBayesian) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="BrS_penetranceBayesian")]), d2$BrS_penetranceBayesian, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

### Predicting Recovery from Inactivation with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r BrS1_lm}
# all predictors
ln_BrS1 <- lm(BrS_penetranceBayesian~., data = subset(d2, select = c(BrS_penetranceBayesian,1 + fin.lass$beta@i)))
summary(ln_BrS1)
foo <- boot(d, function(data,indices)
  summary(lm(BrS_penetranceBayesian~., data = subset(d2[indices,], select = c(BrS_penetranceBayesian, 1+fin.lass$beta@i))))$adj.r.squared,R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))
```

## LQT3

### Parameter Selection for lqt3 Model

```{r LASSO_lqt3}

d2 <- d[, which(names(d) %in% c( "lqt3_penetrance_dist", "lqt3_penetrance_dist_weight", "pamscore", "SIFT.Score", "eaRate", "blastpssm", "NeighborVector", "NeighborCount",
        "provean_score", "polyphen2", "aaneigh", "aaneighvector","LQT_penetranceBayesian", "resnum"))]
d2 <- d2[complete.cases(d2),]

cv.lass <- cv.glmnet( as.matrix(d2[,-which(names(d2)=="LQT_penetranceBayesian")]), d2$LQT_penetranceBayesian) 
fin.lass <- glmnet(as.matrix(d2[,-which(names(d2)=="LQT_penetranceBayesian")]), d2$LQT_penetranceBayesian, lambda = cv.lass$lambda.min)  
fin.lass$beta

```

### Predicting LQT3 with Best Predictors found in Previous Step and bootstrap 95% CIs

```{r lqt3_lm}
# all predictors
ln_lqt3 <- lm(LQT_penetranceBayesian~., data = subset(d2, select = c(LQT_penetranceBayesian, 1 + fin.lass$beta@i)))
summary(ln_lqt3)
foo <- boot(d, function(data,indices)
  summary(lm(LQT_penetranceBayesian~., data = subset(d2[indices,], select = c(LQT_penetranceBayesian, 1+fin.lass$beta@i))))$adj.r.squared,R=1000)
foo$t0
quantile(foo$t,c(0.025,0.975))
```

### Plot Predicted and Experimental Functional Parameters

```{r lqt_raw_plot, echo=TRUE}
# plot relationships between functional parameters and calculated structure-based
# functional parameters.
plot(d$brs1_penetrance_dist, d$BrS_penetranceBayesian, cex=2, lwd=2)
plt.loess(loess(d$BrS_penetranceBayesian~d$brs1_penetrance_dist, span=0.7),ylabel= "Peak Current")

plot(d$lqt3_penetrance_dist, d$LQT_penetranceBayesian, cex=2, lwd=2)
plt.loess(loess(d$LQT_penetranceBayesian~d$lqt3_penetrance_dist, span=0.7),ylabel= "Peak Current")
```

### Plot Predicted and Experimental Vinact

```{r brs_lqt3_exp_pred}
plot(ln_BrS1$fitted.values,ln_BrS1$model$BrS_penetranceBayesian, cex=2, lwd=2, ylim = c(0,max(ln_BrS1$model$BrS_penetranceBayesian)), xlim = c(0, max(ln_BrS1$model$BrS_penetranceBayesian)))
abline(a=0,b=1)

plot(ln_lqt3$fitted.values,ln_lqt3$model$LQT_penetranceBayesian, cex=2, lwd=2, ylim = c(0,max(ln_lqt3$model$LQT_penetranceBayesian)), xlim = c(0, max(ln_lqt3$model$LQT_penetranceBayesian)))
abline(a=0,b=1)
```


# ROCs for predicting LOF based on ipeak current < 50%

```{r ROCs}
source("/Users/Brett/Dropbox/SCN5A/jeff roc fnc.r")

fglm<-d[!is.na(d$ipeak_dist), ]
modfunc <- glm(LOF~blastpssm+eaRate+polyphen2+pamscore+provean_score+SIFT+ipeak_dist, data=fglm, family='binomial')
mod <- glm(LOF~blastpssm+eaRate+polyphen2+pamscore+provean_score+SIFT, data=fglm, family='binomial')
summary(mod)

roc.ci(d$LOF[row.names(d) %in% as.numeric(names(predict(modfunc)))], predict(modfunc))

roc.ci(d$LOF[row.names(d) %in% as.numeric(names(predict(mod)))], predict(mod))

library(pROC)
modfunc1 <- glm(LOF~polyphen2, data = fglm, family = 'binomial')
modfunc2 <- glm(LOF~eaRate, data = fglm, family = 'binomial')
modfunc3 <- glm(LOF~blastpssm, data = fglm, family = 'binomial')
modfunc4 <- glm(LOF~provean_score, data = fglm, family = 'binomial')
modfunc5 <- glm(LOF~SIFT, data = fglm, family = 'binomial')
modfunc6 <- glm(LOF~blastpssm+eaRate+polyphen2+pamscore+provean_score+SIFT, data = fglm, family = 'binomial')
modfunc7 <- glm(LOF~blastpssm+eaRate+polyphen2+pamscore+provean_score+SIFT+ipeak_dist, data = fglm, family = 'binomial')

funs <- list(modfunc2, modfunc3, modfunc4, modfunc5, modfunc6, modfunc7)
colrs <- c("red", "green", "yellow", "orange", "blue", "black")
i=0
par(pty="s")
tmp<-roc(d$LOF[row.names(d) %in% as.numeric(names(predict(modfunc1)))], predict(modfunc1), ci=T)
print(tmp$auc)
print(tmp$ci)
plot.roc(tmp, col = "magenta")
for(li in funs){
  i=i+1
  tmp<-roc(d$LOF[row.names(d) %in% as.numeric(names(predict(li)))], predict(li), ci=T)
  print(tmp$auc)
  print(tmp$ci)
  plot.roc(tmp,add = T, col = colrs[i])
}

```
